# Introduction 

```{r}
#| label: load_packages
#| include: false
library(tidyverse)

```



Do you see any Teletubbies in here? Do you see a slender plastic tag clipped to my shirt with my name printed on it? Do you see a little Asian child with a blank expression on his face sitting outside on a mechanical helicopter that shakes when you put quarters in it? No? Well, that's what you see at a toy store. And you must think you're in a toy store, because you're here shopping for an infant named Jeb.

## Data

Included in this template is a file called `sales.csv`. This contains quarterly data on Sales and Advertising budget for a small company over the period 1981--2005. It also contains the GDP (gross domestic product) over the same period. All series have been adjusted for inflation. We can load in this data set using the following code:

```{r}
#| label: load_data
#| echo: true
#| tbl-cap: this is the data
library(palmerpenguins)

penguins |>
select(species, island) |>
head(2) |>
knitr::kable(format = "latex")


```

Any data you use in your thesis can go into the `data` directory. The data should be in exactly the format you obtained it. Do no editing or manipulation of the data prior to including it in the `data` directory. Any data munging should be scripted and form part of your thesis files (possibly hidden in the output).

## Figures`

@fig-pengs shows time plots of the data we just loaded. Notice how figure captions and references work. Chunk names can be used as figure labels with `fig-` prefixed. Never manually type figure numbers, as they can change when you add or delete figures. This way, the figure numbering is always correct.

```{r}
#| label: fig-pengs
#| fig-cap: "Quarterly sales, advertising and GDP data."


ggplot(penguins, aes(body_mass_g)) + geom_histogram()

```


